---
title: "R Notebook"
output: html_notebook
---

This is the import process

```{r}
library(tidyverse)
library(plotly)
```


```{r}
simulated_patient_data <- read_csv("https://github.com/philbowsher/Foundation-of-the-R-Workflow-workshop-2019-09-06/raw/master/Examples/data/simulated_patient_data.csv")

simulated_patient_data
```

This is the data viz

```{r}
simulated_patient_data %>%
 filter(stop >= "1965-11-10 17:28:26" & stop <= "2020-12-05 11:57:34") %>%
 
    filter(marital %in% "S" | is.na(marital)) %>%
 filter(patient_age >= 56L & patient_age <= 
    111L) %>%
 ggplot() +
 aes(x = race, fill = gender) +
 geom_bar() +
 scale_fill_hue() +
 theme_minimal()
```

Interactive data viz

```{r}

```

ETC

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
